A performance assessment of evolutionary algorithms in volunteer computing environments: the importance of entropy

### 2016-11-13 EvoPar2017/paper.Rnw
Adds references to intro refs #132

\title{A performance assessment of evolutionary algorithms in
  volunteer computing environments}

@@

\begin{abstract}
In a volunteer distributed computing system, users run a program on
their own machine to contribute to a common effort. If the program is
embedded in a web page, collaboration is easy, but also ephemeral. In
this paper, we analyze a volunteer evolutionary computing system called
NodIO, trying to find out a few rules that encourage volunteer
participation and how to make the most of their contributions to the
evolutionary algorithm. We will show different measures of
participation and contribution to the algorithm and how different
volunteer usage patterns and tweaks in the algorithm, such as restarting clients when solution has been found, contribute to
improvements and leveraging of these contributions. 
\end{abstract}

@@

The world wide web provides not only a platform for content
distribution, but also an increasingly reliable and high-performance
operating system for running distributed applications. This is based
in two key things: the Javascript virtual machine every browser runs
and a simplified standard interface for interacting with servers.
Thus creating a distributed computing experiment is just a matter of
making a JavaScript application interchange information with a server,
called REST. From the point of view of the programmer, this involves
relatively common skills and no special libraries, since that
interface is built in the browser, and a simple application that
responds to those requests on the server side; both involve just a few
dozens lines of code additionally to whatever business logic your
application has. But, more importantly and from the point of view of
the user, that application can be run by simply visiting a web page.

>>>>

\title{A performance assessment of evolutionary algorithms in
  volunteer computing environments: the importance of entropy}

@@

\begin{abstract}
In a volunteer distributed computing system, users run a program on
their own machine to contribute to a common effort. If the program is
embedded in a web page, collaboration is straightforward, but also ephemeral. In
this paper, we analyze a volunteer evolutionary computing system called
NodIO, by running several experiments, some of them massive. Our
objective is to discover rules that encourage volunteer
participation and also the interplay of these contributions with the
dynamics of the algorithm itself, making it more or less efficient. We will show different measures of
participation and contribution to the algorithm and how different 
volunteer usage patterns and tweaks in the algorithm, such as
restarting clients when solution has been found, contribute to 
improvements and leveraging of these contributions. We will also try
to find out what is the key factor in the early termination of the
experiments, measuring entropy in the contributions and other large
scale indicators. 
\end{abstract}

@@

The World Wide Web provides not only a platform for content
distribution, but also, thanks to the maturity and reliability of the
HTTP protocol, an increasingly reliable and high-performance
operating system for running distributed applications. Besides the
protocol itself, there are two factors that contribute to this fact:
the Javascript virtual machine every browser runs \cite{paulson2005building}
and the simplified standard interface for interacting with servers
exemplified by the REST application interface convention \cite{masse2011rest}.
Thus creating a distributed computing experiment is just a matter of
making a JavaScript application interchange information with a server,
called REST. From the point of view of the programmer, this involves
relatively common skills and no special libraries, since that
interface is built in the browser, and a simple application that
responds to those requests on the server side; both involve just a few
dozens lines of code additionally to whatever business logic your
application has. But, more importantly and from the point of view of
the user, that application can be run by simply visiting a web page.

### 2016-11-13 EvoPar2017/paper.tex
Adds references to intro refs #132

NodIO needs a fitness function to work with; in this case the classical Trap 
function \cite{Ackley1987} has been used. % I don't think this use of the ; is correct
% Changed to .
The evolutionary algorithm that evaluates that function runs in the
browser, but the server needs to know when the solution has been
found, so a function that checks termination condition is also included in the server, as a configuration
option. In all cases we are using 50 Traps, a problem
that is difficult enough to need the intervention of several users for
an extended amount of minutes.
For every new individual sent by the clients to the cache, several
% We have not presented the "cache",  only the server and
% ..storing the incoming chromosomes in a data structure
% Im changing over there to cache
% That's been changed - JJ
pieces of metadata were stored: a time stamp, the client IP, the chromosome and
fitness value, the cache size in that particular moment, and also if that
individual actually updated the cache or not.

>>>>

NodIO needs a fitness function to work with; in this case the classical Trap 
function \cite{Ackley1987} has been used. 
The evolutionary algorithm that uses Trap as fitness function is
completely run in the
browser, but the server needs to know when the solution has been
found, so a subroutine that checks if the solution been found  is also included in the server, as a configuration
option. In all cases we are using 50 Traps, a problem
that is difficult enough to need the intervention of several users for
an extended amount of minutes.
For every new individual sent by the clients to the cache, several
pieces of metadata were stored: a time stamp, the client IP, the chromosome and
fitness value, the cache size in that particular moment, and also if that
individual actually updated the cache or not.
